Tight Bounds for Dynamic Balanced Graph Partitioning

### 2020-05-09 paper/disc20clustering.tex
Comments

\maciek{"at the same time. However" One sentence? joined with "but"}

@@

@@

>>>>

@@

\maciek{Suggestion: "Note that \OPT cannot have both..." (till the end of paragraph) You told me this in one sentence during the call. Maybe use the same formulation? I feel like one sentence can be enough to explain this}

@@

\maciek{OPT's cost formula: make it one line by removing the expression with minimums. Move minimums to the paragraph text, by immediatelly expanding minimums (two steps in paragraph, instead of in the formula)}
